Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants\thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN 712689 SC$^2$.}

### 2017-05-01 cav2017/cav2017.tex
cite for completeness threshold

{\em The first approach} uses a na\"ive technique that starts by
devising a digital controller that stabilizes the system while remaining
safe for a pre-selected time horizon and a single initial state; then, it
verifies unbounded safety by unfolding the dynamics of the system,
considering the full hyper-cube of initial states, and checking a {\em
completeness threshold}, i.e., the number of iterations required to
sufficiently unwind the closed-loop state-space system such that the
boundaries are not violated for any larger number of iterations.  As~it
requires unfolding up to the completeness threshold, this approach
is computationally expensive.

@@

An overview of the algorithm for controller synthesis is given in
Fig.~\ref{fig:CEGIS-precision-increment}.  One important observation is that
we verify and synthesize a controller over $k$ time steps.  We~then compute
a completeness threshold, $\overline{k}$, for this controller, and verify
correctness for $\overline{k}$ time steps.  Essentially, $\overline{k}$ is
the number of iterations required to sufficiently unwind the closed-loop
state-space system such that the boundaries are not violated for any
$k{>}\overline{k}$.

@@

We have presented two automated approaches to synthesize digital
state-feedback controllers that ensure both stability and safety over the
state-space representation.  The first approach relies on unfolding of the
closed-loop model dynamics up to a completeness threshold, whilst the second
one applies abstraction refinement and acceleration to increase speed whilst
retaining soundness.
%
Both approaches are novel within the control literature: they give a fully
automated synthesis method that is algorithmically and numerically sound,
considering various error sources in the implementation of the digital
control algorithm and in the computational modeling of plant dynamics.
%
Our experimental results show that both approaches are able to synthesize
stable controllers for most benchmarks within a reasonable amount of time
fully automatically.  In particular, both approaches complement each other
and together solve all benchmarks, which have been derived from the control
literature.

>>>>

{\em The first approach} uses a na\"ive technique that starts by devising a
digital controller that stabilizes the system while remaining safe for a
pre-selected time horizon and a single initial state; then, it verifies
unbounded safety by unfolding the dynamics of the system, considering the
full hyper-cube of initial states, and checking a {\em completeness
threshold}~\cite{DBLP:conf/vmcai/KroeningS03}, i.e., the number of
iterations required to sufficiently unwind the closed-loop state-space
system such that the boundaries are not violated for any larger number of
iterations.  As~it requires unfolding up to the completeness threshold, this
approach is computationally expensive.

@@

An overview of the algorithm for controller synthesis is given in
Fig.~\ref{fig:CEGIS-precision-increment}.  One important observation is that
we verify and synthesize a controller over $k$ time steps.  We~then compute
a completeness threshold~\cite{DBLP:conf/vmcai/KroeningS03}, $\overline{k}$,
for this controller, and verify correctness for $\overline{k}$ time steps. 
Essentially, $\overline{k}$ is the number of iterations required to
sufficiently unwind the closed-loop state-space system such that the
boundaries are not violated for any $k{>}\overline{k}$.

@@

We have presented two automated approaches to synthesize digital
state-feedback controllers that ensure both stability and safety over the
state-space representation.  The first approach relies on unfolding of the
closed-loop model dynamics up to a completeness threshold, while the second
one applies abstraction refinement and acceleration to increase speed whilst
retaining soundness.
%
Both approaches are novel within the control literature: they give a fully
automated synthesis method that is algorithmically and numerically sound,
considering various error sources in the implementation of the digital
control algorithm and in the computational modeling of plant dynamics.
%
Our experimental results show that both approaches are able to synthesize
stable controllers for most benchmarks within a reasonable amount of time
fully automatically.  In particular, both approaches complement each other
and together solve all benchmarks, which have been derived from the control
literature.
